---
title: "Project 4"
author: "Sean Carey"
date: "12/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(ZillowR)
library(tidyverse)
library(xml2)
library(XML)
library(purrr)
library(randomForest)
set.seed(5415)
```
##PART 1: Prepare the Data


### Read in LA Address Data

The address data is stored as a csv and will be read into R as a data frame

```{r read address data, eval=FALSE, include=FALSE}
La_Address <- read_csv("rows.csv")
```

### Sample Addresses

Take a random sample of 5000 addresses

```{r pressure, echo=FALSE, eval=FALSE}
LA_SAMPLE <- LA_Address[sample(nrow(LA_Address),5000), ]
```

### Create Function to combine address fields  

All of the needed address fields are stored in separate columns of the La_Address. This function will take all 5000 of the sampled LA Addresses and combine them into a single character vector.
```{r Parse Address Function, eval=FALSE}
Parse_Address <-function (z) { 
  DF <- setNames(data.frame(matrix(ncol = 1, nrow = 0)), c("address"))
   i <- 1
   
    while(i <= nrow(z)){
   x <- paste0(z[i,4]," ",z[i,5]," ",z[i,6]," ",z[i,7]," ",z[i,8]," ",z[i,9], " ") 
   x <- str_replace_all(x," NA ", " "); 
   DF[i,1] <-x; i <- i+1
   
    }  
return(as.data.frame(DF))
}

#run the sampeld LA Addresses thru the function
## The vector is saved as a data frame for ease of use
LA_SAMPLE_VECTOR <- Parse_Address(LA_SAMPLE)





```

### ZILLOW API Function 

The Zillow API allows us to us to query addresses on the Zillow website and get a list containing an XML of the ZILLOW data for the address.  

This function will read an address, queary ZILLOW using the ZILLOW API, extract the desired information from the returned XML and save it as a row in a data frame. 

```{r ParseZillow Function, eval=FALSE}

Parse_Zillow <- function(x){
   #create empty data frame
   X <- setNames(as.data.frame(matrix(ncol = 12, nrow = 1)), c("street","zip", "city","Use_Code", "Tax_Year", "Tax_Value","year_built", "lot_size", "finished_sq_feet", "bathrooms","bedrooms", "zestimate"))
   #query the API save return as "reply"
   reply = RCurl::getForm("http://www.zillow.com/webservice/GetDeepSearchResults.htm", 'zws-id' = "X1-ZWz1gsahvqczkb_376md",
                   address = x,
                   citystatezip = "Los Angeles, CA")
   #extract the XML portion of "reply"
   y <- xmlTreeParse(reply,asText = TRUE, useInternalNodes = TRUE)
   #save returned http code as "code"
   code <-xmlValue(y[["//code"]])
   #if 508 is returned then the zillow does not have that address. Results in a row of NA's 
   if(code == "508")  X[1,1:12] <- "NA"
      
      #use xpathCheck to extract the desired information
      #saveit it as a variable in a data frame
      
          X[1,1] <- xpathCheck(y, "//street")
          X[1,2] <- xpathCheck(y,"//zipcode") 
          X[1,3] <-   xpathCheck(y,"//city")
          X[1,4] <-  xpathCheck(y,"//useCode")
          X[1,5] <- xpathCheck(y,"//taxAssessmentYear")
          X[1,6] <- xpathCheck(y,"//taxAssessment")
          X[1,7] <- xpathCheck(y,"//yearBuilt")
          X[1,8] <- xpathCheck(y,"//lotSizeSqFt")
          X[1,9] <- xpathCheck(y,"//finishedSqFt")
          X[1,10] <- xpathCheck(y,"//bathrooms")
          X[1,11] <- xpathCheck(y,"//bedrooms")
          X[1,12] <- xpathCheck(y,"//amount")
          
   
  return(X)
}


#Use map_df from the PURR packackage to run each address in the LA_SAMPLE data frame thru the Parse_Zillow function
#map_df was chosen because it returns a data frame

ZILLOW_FULL <- map_df(LA_SAMPLE_VECTOR[1:4000, ], Parse_Zillow)

write_csv(ZILLOW_FULL, "ZILLOW_FULL_DATA.csv")
```


```{r}

# drop rows with missng mavlues
MODEL_FULL <- ZILLOW_FULL %>% as.tibble() %>% select(Use_Code:zestimate)

MODEL_FULL$Use_Code <- forcats::as_factor(MODEL_FULL$Use_Code)
MODEL_FULL$Tax_Year <- as.numeric(MODEL_FULL$Tax_Year)
MODEL_FULL$Tax_Value <- as.numeric(MODEL_FULL$Tax_Value)
MODEL_FULL$year_built <- as.numeric(MODEL_FULL$year_built)
MODEL_FULL$lot_size <- as.numeric(MODEL_FULL$lot_size)
MODEL_FULL$finished_sq_feet <- as.numeric(MODEL_FULL$finished_sq_feet)
MODEL_FULL$bathrooms <- as.numeric(MODEL_FULL$bathrooms)
MODEL_FULL$bedrooms <- as.numeric(MODEL_FULL$bedrooms)
MODEL_FULL$zestimate <- as.numeric(MODEL_FULL$zestimate)

MODEL_FULL <- drop_na(MODEL_FULL)

write_csv(MODEL_FULL, "ZILLOW_DATA.csv")

```

##Split Zillow data into Training and Test datasets


```{r Split Model Dataset}

TRAIN <- sample(1:nrow(MODEL_FULL), size = nrow(MODEL_FULL)*0.8)
TEST <- dplyr::setdiff(1:nrow(MODEL_FULL), TRAIN)

#create training and test data sets
MODEL_TRAIN <-  MODEL_FULL[TRAIN, ]
MODEL_TEST <- MODEL_FULL[TEST, ]


```

##Part II: The Analysis  

  We will fit the Zillow data to a bagged regression tree using sequential fitting/predicting and Parallel fitting/predicting

### Sequentially Fit Bagged Regression Tree 


```{r Sequential Tree}
S_BAG_FIT <- randomForest::randomForest(zestimate ~ ., data = MODEL_TRAIN, mtry = ncol(MODEL_TRAIN) - 1, 
											 ntree = 2000, importance = TRUE)
S_BAG_PRED <- predict(S_BAG_FIT, newdata = dplyr::select(MODEL_TEST, -zestimate))

S_BAG_RMSE <- sqrt(mean((S_BAG_PRED - MODEL_TEST$zestimate )^2))

S_BAG_RMSE

cbind(S_BAG_PRED, MODEL_TEST$zestimate )

```






